Basics of Hardware Cache Optimization

### 2017-06-05 tex/basic-concepts/lines.tex
Swap "Prefetching" and "Cache Line" sections
Expand content, revise, tweak

\subsection{Cache Line} % or Cache Block
% https://en.wikipedia.org/wiki/CPU_cache#Cache_entries
%
% > On x86/x64, cache line is 64 bytes for many years now.
%      -- http://ithare.com/c-for-games-performance-allocations-and-data-locality/
% > In early caches these lines were 32 bytes long; nowadays the norm is 64 bytes.
%      -- Drepper, p. 15
% > It is not possible for a cache to hold partial cache lines.
%      -- Drepper, p. 16
% > A cache line is the "unit" of data you transfer to a cache.
%      -- http://www.cs.umd.edu/class/sum2003/cmsc311/Notes/Memory/introCache.html
\emph{Cache lines} or \emph{cache blocks} are the unit of data transfer between main
memory and cache.  They have a fixed size, which has been \say{64 bytes for many years} on
x86/x64 CPUs~\cites{ithare-paadl}[\href{https://youtu.be/WDIkqP4JbkE?t=21m41s}{21:41}]
{scott-meyers-talk}.%
\footnote{%
% > The original Pentium 4 processor also had an eight-way set associative L2 integrated
% > cache 256 KB in size, with 128-byte cache blocks.
%      -- https://en.wikipedia.org/wiki/CPU_cache#Example
% TODO: what about the block size of main memory?  Should it be the same?
Line sizes aren't \emph{necessarily} \alts{identical, homogenous} among a CPU's caches.
The Intel Pentium 4 processor had an \texttt{L1d} cache with \say{64 bytes per cache
line}~\cite[p.~9]{pentium4} but an \texttt{L2} cache with \say{128 bytes per cache
line}~\cite[p.~11]{pentium4}.}
\begin{comment}
   \multiplefootnoteseparator%
   % See <https://tex.stackexchange.com/a/71015>.
   \footnote{This can also be checked on the command line:
   \mintinline{bash}{cat /proc/cpuinfo | grep cache_alignment}}
\end{comment}
% > It means that as soon as you've accessed any single byte in a cache line, all the
% > other 63 bytes are already in L1 cache
%      -- http://ithare.com/c-for-games-performance-allocations-and-data-locality/
\alts{%
   This means accessing a single uncached 32-bit integer entails loading another 60
   adjacent bytes.,
   {This means when a single byte has to be loaded, another 63 adjacent bytes will be as
   well.},
   {When, for example, accessing a single byte that isn't already cached, another 63
   adjacent bytes will be loaded.}
}
% Even when compiling C++ for 64-bit systems, `int` is typically 32-bit.

@@

% XXX: hacks!  Explicit placement specifier without `t` (top) to prevent the figure from
% interrupting the source code listing.
\begin{figure}[hbp]
   \centering
   \begin{tikzpicture}
      \datavisualization
      [scientific axes=clean,
       x axis={logarithmic,
               ticks={major={at={1 as \textbf{1}, 2 as \textbf{2}, 4 as \textbf{4},
                                 8 as \textbf{8}, 16, 64, 256, 1024}},
                      minor={at={32, 128, 512}}},
               label={Step size}, length=0.8\textwidth},
       y axis={logarithmic,
               % ticks={major={at={4, 16, 64, 256}}, minor={at={8, 32, 128}}},
               % ticks={major={at={6, 12, 24, 48, 92, 184}}},
               ticks={major={at={10, 20, 40, 80, 160, 320}}},
               label={Processor time (ms)}, length=6cm},
       visualize as scatter,
       scatter={style={mark=*, mark options={scale=.65}}}]
         % See <https://tex.stackexchange.com/q/198323>.
         data [read from file=line-size/line-size.csv, separator=\space];
   \end{tikzpicture}
   \caption{Processor times for running \cref{lst:line-size}}
   \label{fig:line-size}
\end{figure}

>>>>

\subsection{Cache Line} % or Cache Block
% https://en.wikipedia.org/wiki/CPU_cache#Cache_entries
%
% > On x86/x64, cache line is 64 bytes for many years now.
%      -- http://ithare.com/c-for-games-performance-allocations-and-data-locality/
% > In early caches these lines were 32 bytes long; nowadays the norm is 64 bytes.
%      -- Drepper, p. 15
% > It is not possible for a cache to hold partial cache lines.
%      -- Drepper, p. 16
% > A cache line is the "unit" of data you transfer to a cache.
%      -- http://www.cs.umd.edu/class/sum2003/cmsc311/Notes/Memory/introCache.html
\emph{Cache lines} or \emph{cache blocks} are the unit of data transfer between main
memory and cache.  They have a fixed size, which has been \say{64 bytes for many years} on
x86/x64 CPUs~\cites{ithare-paadl}[\href{https://youtu.be/WDIkqP4JbkE?t=21m41s}{21:41}]
{scott-meyers-talk}.%
\footnote{%
% > The original Pentium 4 processor also had an eight-way set associative L2 integrated
% > cache 256 KB in size, with 128-byte cache blocks.
%      -- https://en.wikipedia.org/wiki/CPU_cache#Example
% TODO: what about the block size of main memory?  Should it be the same?
Line sizes aren't \emph{necessarily} \alts{identical, homogenous} among a CPU's caches.
The Intel Pentium 4 processor had an \gls{l1d} cache with \say{64 bytes per cache
line}~\cite[p.~9]{pentium4} but an \gls{l2} cache with \say{128 bytes per cache
line}~\cite[p.~11]{pentium4}.}
\begin{comment}
   \multiplefootnoteseparator%
   % See <https://tex.stackexchange.com/a/71015>.
   \footnote{This can also be checked on the command line:
   \mintinline{bash}{cat /proc/cpuinfo | grep cache_alignment}}
\end{comment}
% > It means that as soon as you've accessed any single byte in a cache line, all the
% > other 63 bytes are already in L1 cache
%      -- http://ithare.com/c-for-games-performance-allocations-and-data-locality/
\alts{%
   This means accessing a single uncached 32-bit integer entails loading another 60
   adjacent bytes.,
   {This means when a single byte has to be loaded, another 63 adjacent bytes will be as
   well.},
   {When, for example, accessing a single byte that isn't already cached, another 63
   adjacent bytes will be loaded.}
}
% Even when compiling C++ for 64-bit systems, `int` is typically 32-bit.

@@

% XXX: hacks!  Explicit placement specifier without `t` (top) to prevent the figure from
% interrupting the source code listing.
\begin{figure}%[hbp]
   \centering
   \begin{tikzpicture}
      \datavisualization
      [scientific axes=clean,
       x axis={logarithmic,
               ticks={major at={1, 2, 4, 8 as \textbf{8}, 16, 64, 256, 1024},
                      minor at={32, 128, 512}},
               grid={at=8},
               label={Step Size}, length=0.8\textwidth},
       y axis={logarithmic,
               % ticks={major={at={4, 16, 64, 256}}, minor={at={8, 32, 128}}},
               % ticks={major={at={6, 12, 24, 48, 92, 184}}},
               ticks={major at={10, 20, 40, 80, 160, 320}},
               grid=at ticks,
               label={Processor Time (ms)}, length=6cm},
       visualize as scatter,
       scatter={style={mark=*, mark options={scale=.65}}}]
         % See <https://tex.stackexchange.com/q/198323>.
         data [read from file=line-size/line-size.csv, separator=\space];
   \end{tikzpicture}
   \caption{Processor Times for Running \Cref{lst:line-size}}
   \label{fig:line-size}
\end{figure}

### 2017-06-05 tex/basic-concepts/prefetching.tex
Create style for the two access time scatter plots
Replace two tikzpicture environments with \tikz
I think these uses of \tikz are a shorter and semantically identical
alternative to using the tikzpicture environment.  See the second
paragraph of section 2.3 "Straight Path Construction" (page 31) of the
TikZ and PGF manual (version 3.0.1a).
Expand content, revise, tweak

% \cref{lst:TODO} is
Consider
a simplified version of \cref{lst:access-times} that, instead of using random accesses,
simply walks over the array sequentially.  It still follows the pointers to do this, but
the array is no longer shuffled.

% \emph{Cache prefetching} is a technique by which CPUs recognize predictable access
% patterns (for instance sequential access to an array)... TODO

>>>>

Consider a simplified version of \cref{lst:access-times} that, instead of using random
accesses, simply walks over the array sequentially.  It still follows the pointers to do
this, but the array is no longer shuffled.  The results of profiling this new program
\alts{as, in the same way as, just as, like} \cref{lst:access-times} before are
\alts{plotted, shown} in \cref{fig:seq-access-times}.%
\footnote{%
   \Vref{tab:seq-access-times} shows the numerical results.%
   % Numerical results are shown in \vref{tab:seq-access-times}.%
}

% XXX: consider possible effects of [software prefetching][1].  I think GCC doesn't enable
% this type of optimization unless `-fprefetch-loop-arrays` is explicitly specified; i.e.,
% none of the `-O` levels enables it.  See [2].  XXX: WRONG:
%
%    $ gcc -O2 -Q --help=optimizers | grep prefetch
%    -fprefetch-loop-arrays                [enabled]
%
% This is also interesting:
%
%    $ diff <(gcc -Q --help=optimizers) <(gcc -O2 -Q --help=optimizers)
%
% [1]: https://en.wikipedia.org/wiki/Cache_prefetching#Compiler_directed_prefetching
% [2]: https://gcc.gnu.org/onlinedocs/gcc/Optimize-Options.html#Optimize-Options

% XXX.  This section may be misleading: it could seem like it suggests all of the measured
% speedup is a result of prefetching.  It is a huge contributor, though.  The result from
% accessing all data in a cache line should at most be that of dividing the initial main
% memory access (about 200 cycles) between 8 separate reads.  Since reads from L1d still
% take about 3 cycles:
%    (200 + 7 * 3) / 8 = 221 / 8 = 27.625
% Since the actual numbers aren't much above 6 cycles, prefetching still has a huge effect
% (6.3 / 27.625 ~= 22.8 %).
\x{Compared to the nearly 200 cycles the random accesses caused, ...}
Until the working set size \alts{matches that of, exceeds} the \gls{l1d}, the access times
are virtually unchanged at 3 cycles, but exceeding the \gls{l1d} and hitting the \gls{l2}
\alts{increases this by, adds} no more than \alts{a single, one} cycle.
More \alts{strikingly, remarkably}, \alts{exceeding} the \gls{l2}
\alts{%
   has \alts{similarly limited, comparably little} effect,
   is \alts{com:comparably, similarly} inconsequential,
}.
The access time plateaus not much above 6 cycles \x{now} --- about \alts{\SI{3}{\percent},
3\%, 3 \%} of the maximum we saw for random reads.
 % This is in large part thanks to \emph{prefetching}.
Much of this can be explained by the improved use of cache lines: the penalty of loading a
cache line is distributed among 8 accesses now.  This \alts{%
   could at \alts{best, most} get us down to,
   can not get us down to less than,
}
\SI{12.5}{\percent}.
% \alts{In large part, To a high degree, To a great extend}, the improvements are due to
% \emph{prefetching}.
The missing improvements are due to \emph{prefetching}.

Prefetching is a \x{heuristic} technique by which CPUs \alts{predict \x{certain},
recognize predictable} access patterns and \alts{%
   preemptively push cache lines up the memory hierarchy before the program needs them,
   speculatively load data before the program needs it,
}.
% > This can work well only when the memory access is predictable, though.
%      -- Drepper, p. 23
% > Currently prefetch units do not recognize non-linear access patterns.
%      -- Drepper, p. 60
\alts{%
   {This can not work unless cache line access is predictable, though, which basically
   means \x{sequential} linear},
   {For this to work, cache line access has to be predictable, which usually means
   sequential},
   % This requires,
   % This only works if,
}%
~\cite[60]{drepper2007}.%
\footnote{%
   As an example, the most complicated \emph{stride pattern} my laptop's CPU can detect is
   % https://en.wikipedia.org/wiki/Hyphen#Suspended_hyphens
   one that skips over at most 3 cache lines (for- or backwards) and may alternate strides
   (e.g.  +1, +2, +1, +2, \ldots)~\cite[278]{14h}.
}

% > The purpose of prefetching is to hide the latency of a memory access.
% ...
% > Prefetching has one big weakness: it cannot cross page boundaries.
% ...
% > [R]egardless of how good the prefetcher is at predicting the pattern, the program will
% > experience cache misses at page boundaries
%      -- Drepper, p. 60

% > Prediction or explicit prefetching might also guess where future reads will come from
% > and make requests ahead of time; if done correctly the latency is bypassed altogether.
%      -- https://en.wikipedia.org/wiki/Cache_(computing)#Latency

% > [P]refetching [can] remove some of the costs of accessing main memory since it happens
% > asynchronously with respect to the execution of the program. It can [...] make the
% > cache appear bigger than it actually is.
%      -- Drepper, p. 14
Prefetching happens asynchronously to normal program execution~\cite[14]{drepper2007}
% > [T]he processor is able to hide most of the main memory and even L2 access latency by
% > prefetching cache lines into L2 and L1d.
%      -- Drepper, p. 23
and can therefore\x{, in principle,}\ almost completely hide the main memory latency%
~\cite[23]{drepper2007}.
This is not quite what we observe in \cref{fig:seq-access-times} because the CPU
\alts{performs, has to perform} little enough work for memory bandwidth to become the
bottleneck.
% XXX: the peak transfer rate of my ThinkPad's memory (DDR3-1333, I think) is much higher
% (should be 10666.67 MB/s) than the rate observed in this test (about 2 GB/s).
%    8 B / (6.2 / 1.65 GHz) = 8 * 1.65 GB/s / 6.2 = 105.6 ~= 2.13 GB/s
% What limits it?  How to achieve the theoretical maximum?  My understanding is that
% sequential read access like this should pretty much be the most efficient use of RAM
% possible.
%
% I compiled and ran the [STREAM][1] benchmark ([FAQ][2]) by [Dr. John D. McCalpin][3]
% recommended [here][4].  It gives similarly low data rates.
%
% [1]: https://www.cs.virginia.edu/stream/
% [2]: https://www.cs.virginia.edu/stream/ref.html
% [3]: http://www.cs.virginia.edu/~mccalpin/
% [4]: http://www.admin-magazine.com/HPC/Articles/Finding-Memory-Bottlenecks-with-Stream
% [5]: https://software.intel.com/en-us/articles/optimizing-memory-bandwidth-on-stream-triad
% [6]: https://www.nersc.gov/users/computational-systems/cori/nersc-8-procurement/trinity-nersc-8-rfp/nersc-8-trinity-benchmarks/stream/
% [7]: https://en.wikipedia.org/wiki/Memory_bandwidth
%
% TODO: I also tried [bandwidth](http://zsmith.co/bandwidth.html).
Adding some expensive operations like integer divisions every loop iteration changes that
and \alts{effectively, almost completely} levels the cycles spend per iteration across all
working set sizes.%
% I tested this.  The difference between L1d and L2 virtually disappears (~0.01 cycles)
% and exceeding the L2 increases the time per element by a single cycle.
\footnote{%
   % TODO.
   See \vref{fig:seq-access-cpu-bound}.
}

% Ubiquitous.

% > Hardware based prefetching is typically accomplished by having a dedicated hardware
% > mechanism in the processor that watches the stream of instructions or data being
% > requested by the executing program, recognizes the next few elements that the program
% > might need based on this stream and prefetches into the processor's cache.
%      -- https://en.wikipedia.org/wiki/Cache_prefetching#Types_of_cache_prefetching
\alts{What I described so far is, So far I described} \emph{hardware} prefetching.  It
uses dedicated silicon to automatically detect access patterns.  There is also
\emph{software} prefetching, which is triggered by special machine instructions that may
be inserted by the compiler or manually by the programmer.  Software prefetching is
discussed in~\cite{drepper2007}.

% > The idea of [the _mm_prefetch() intrinsic] function (actually an asm instruction from
% > x86/x64 instruction set) is to inform CPU that you're about to need certain memory
% > location.
%      -- http://ithare.com/c-for-games-performance-allocations-and-data-locality/2/

% https://gcc.gnu.org/onlinedocs/gcc/Optimize-Options.html#index-fprefetch-loop-arrays

% > Most of the time, prefetch just silently works behind the scenes, and I didn't see
% > cases when messing with prefetch at application-level would be worth the trouble.  At
% > least in theory, however, such cases do exist.
%      -- http://ithare.com/c-for-games-performance-allocations-and-data-locality/2/

% > The source for the prefetch operation is usually main memory.
%      -- https://en.wikipedia.org/wiki/Cache_prefetching

\begin{figure}
   \centering
   \tikz \datavisualization[array size vs cycles plot]
      data [read from file=seq-access-times/access-times.csv, separator=\space];
   \caption{Access Times for Sequential Reads}
   \label{fig:seq-access-times}
\end{figure}

% \begin{figure}
%    \centering
%    \tikz \datavisualization[array size vs cycles plot]
%       data [read from file=seq-access-times/step8/access-times.csv, separator=\space];
%    \caption{TODO}
%    \label{fig:seq8-access-times}
% \end{figure}

### 2017-06-05 tex/methodology.tex
Use varioref in addition to hyperref and cleveref
https://ctan.org/pkg/varioref
Expand content, revise, tweak

@@

% Performance Analysis; Run Time Analysis; Timing Methodology; Profiling Pitfalls; Run
% Time Measuring; Benchmarking Methodology; Performance Monitoring
\section{[TODO] Profiling Methodology}
\label{app:meth}

Plenty of things can go wrong when
profiling.
% measuring \alts{execution, run} times.
These are the ones I was aware of and tried to account for while doing measurements for
this \article.
\begin{itemize}
   \item \emph{CPU frequency scaling and boosting}.
      CPU frequencies are usually dynamic these days and automatically adjusted based on
      at least workload and temperature.  This should be disabled when measuring execution
      times.
      \begin{minted}[autogobble]{text}
         # TODO
      \end{minted}
      % See [5].  Not a problem when measuring cycles.
   \item \emph{Interrupts and context switches.}  The process being timed has to share
      resources with other processes and the operating system.  A context switch will not
      only increase wall time, it will also increase cycles because of TLB flushes and
      cache evictions. % See <https://en.wikipedia.org/wiki/Context_switch>.

@@

General mitigation/alleviation strategy: take the minimum execution time of \alts{all, a
number of} runs; all noise is additive (TODO: not the one caused by the cache being hot).
% See [7].

@@

Frequency scaling isn't a problem here.  I used the \mintinline{text}{ocount(1)} event
counting tool added to the OProfile (TODO: cite) project in version 0.9.9.  [TODO] This
uses \emph{hardware performance counters}.
% `perf(1)` seems to be a newer alternative to OProfile [8].

\begin{minted}[autogobble]{text}
   ophelp
   sudo chrt -f 99 ocount -e CPU_CLK_UNHALTED program
\end{minted}

TODO~\cite[78\psqq]{drepper2007}.

% [1]:  https://en.wikipedia.org/wiki/Profiling_(computer_programming)
% [2]:  https://en.wikipedia.org/wiki/Processor_affinity
% [3]:  https://en.wikipedia.org/wiki/OProfile
% [4]:  https://en.wikipedia.org/wiki/Perf_(Linux)
% [5]:  https://github.com/JuliaCI/BenchmarkTools.jl/blob/master/doc/linuxtips.md
% [6]:  http://stackoverflow.com/q/9006596 "On `/usr/bin/time` for benchmarks and `perf`"
% [7]:  https://youtu.be/vrfYLlR8X8k "Andrei Alexandrescu - Writing Fast Code"
% [8]:  http://oprofile-list.sf.narkive.com/rVbJlHdX/oprofile-vs-perf
% [9]:  http://oprofile.sourceforge.net/about/
% [10]: https://en.wikipedia.org/wiki/Hardware_performance_counter
% [11]: http://oprofile.sourceforge.net/doc/index.html

>>>>

% Performance Analysis; Run Time Analysis; Timing Methodology; Profiling Pitfalls; Run
% Time Measuring; Benchmarking Methodology; Performance Monitoring
\section{Profiling Methodology}
\label{app:meth}

@@

\begin{comment}
Plenty of things can go wrong when \alts{profiling, measuring \alts{execution, run}
times}.  These are the ones I was aware of and tried to account for while doing
measurements for this \article.
\begin{itemize}
   \item \emph{CPU frequency scaling and boosting}.
      CPU frequencies are usually dynamic these days and automatically adjusted based on
      at least workload and temperature.  This should be disabled when measuring execution
      times.  I used the cpupower(1) program.
      % See <https://wiki.archlinux.org/index.php/CPU_frequency_scaling> and
      % <https://github.com/torvalds/linux/tree/master/tools/power/cpupower>.
      \begin{minted}[autogobble]{text}
         # cpupower frequency-set -g performance
         $ ./benchmark
         # cpupower frequency-set -g ondemand
      \end{minted}
      %stopzone
      % See [5].  Not a problem when measuring cycles.
   \item \emph{Interrupts and context switches.}  The process being timed has to share
      resources with other processes and the operating system.  A context switch will not
      only increase wall time, it will also increase cycles because of TLB flushes and
      cache evictions. % See <https://en.wikipedia.org/wiki/Context_switch>.

@@

General mitigation/alleviation strategy: take the minimum execution time of \alts{all, a
number of} runs; all noise is additive (TODO: not the one caused by the cache being hot).
% See [7].
\end{comment}

All programs were compiled and run on Linux using the \gls{gcc} with
\mintinline{text}{-O2} and \mintinline{text}{-march=native}.
% Additionally,
I disabled CPU frequency scaling with \mintinline{text}{cpupower(1)},
% See <https://wiki.archlinux.org/index.php/CPU_frequency_scaling>.
reduced the number of running processes,%
\footnote{%
   I stopped Firefox (which added visible noise) and the X server, for example.
}
% (e.g. leaving Firefox open in the background added lots of noise),
and assigned a high priority to the benchmark process with the \mintinline{text}{chrt(1)}
command.

The \emph{\href{https://github.com/meribold/cache-seminar-paper/blob/master/makefile}
{makefile}} used to compile and run the measurements as well as the full source code of
the programs is available \alts{here, on GitHub}:
\url{https://github.com/meribold/cache-seminar-paper}.

@@

% Frequency scaling is still a problem here.  For example, when the program is memory
% bound, it may take fewer cycles at a lower frequency while completing in the same wall
% time.  I.e., not everything is proportional to CPU frequency.

% > OProfile leverages the hardware performance counters of the CPU.
%      -- http://oprofile.sourceforge.net/about/

% > `ocount` is an OProfile tool that can be used to count native hardware events
% > occurring in [...] a specific application.
%      -- http://oprofile.sourceforge.net/doc/getting-started-with-ocount.html

% A list of AMD family 14h CPU performance counters is available at [1].  `ophelp(1)` can
% also be used.
% [1]: http://oprofile.sourceforge.net/docs/amd-family14h-events.php

I used the \mintinline{text}{ocount(1)} event counting tool added to the
\citetitle{oprofile}~\cite{oprofile} project in version 0.9.9.
% `perf(1)` seems to be a newer alternative to OProfile [8].  TODO: use it?
%
% > Newer CPU models support a hardware performance counter mode which uses hardware logic
% > to record events without any active code needed
%      -- https://en.wikipedia.org/wiki/OProfile
It uses \emph{hardware performance counters}%
\footnote{%
   \url{https://en.wikipedia.org/wiki/Hardware_performance_counter}
}
to provide low-overhead performance information without source code modifications.
\alts{%
   {Essentially, this is the procedure:},
   The \x{exact} process is more or less
}

% diff <(gcc -march=native -E -v - </dev/null 2>&1) <(gcc -E -v - </dev/null 2>&1)
% gcc -O2 -fno-prefetch-loop-arrays -Q --help=optimizers

\begin{minted}[autogobble]{text}
   $ gcc -march=native -O2 program.c
   # cpupower frequency-set -g ondemand
   # chrt -f 99 ocount -e CPU_CLK_UNHALTED ./a.out
\end{minted}
%stopzone

% ~\cite[78\psqq]{drepper2007}.

% [1]: https://en.wikipedia.org/wiki/Profiling_(computer_programming)
% [2]: https://en.wikipedia.org/wiki/Processor_affinity
% [3]: https://en.wikipedia.org/wiki/OProfile
% [4]: https://en.wikipedia.org/wiki/Perf_(Linux)
% [5]: https://github.com/JuliaCI/BenchmarkTools.jl/blob/master/doc/linuxtips.md
% [6]: http://stackoverflow.com/q/9006596 "On `/usr/bin/time` for benchmarks and `perf`"
% [7]: https://youtu.be/vrfYLlR8X8k "Andrei Alexandrescu - Writing Fast Code"
% [8]: http://oprofile-list.sf.narkive.com/rVbJlHdX/oprofile-vs-perf
% [9]: https://serverfault.com/q/161008
%      "What is the difference between renice and chrt commands in Linux?"
